Model of lens candidates from Space Warps CFHTLS

### 2016-07-26 paper2.tex
added subsampling text

@@

In a previous paper \cite{2015MNRAS.447.2170K} we identified the problem of the tendency of the models to be too shallow.
We pinned down the problem to the central region and are confident to have it fixed with enabling sub pixel sampling in the central area.
The software allows for subsampling parameters of radius of pixels $r_\text{subs}$ and amount of subpixels per pixel $n_\text{subs}$.
Figure~\figref{subsampling} shows the results of different settings for $r_\text{subs}$ and $n_\text{subs}$.
We can see that even the computationally least expensive settings of $r_\text{subs}=1$ and $n_\text{subs}=3$ leads to drastically improved profiles.

\begin{figure}
  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
  \includegraphics[width=\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
  \caption{Same sim as in Figure~3 in the earlier paper.}
  \label{fig:subsampling}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_11_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_13_hires_comparison}
  \includegraphics[width=.9\linewidth]{img/hires_comparison/ASW000102p_6941_33_hires_comparison}
  \caption{Model improvement resulting from using smaller mass tiles
    in the inner region of the mass model.  Shown here are the average
    enclosed $\kappa$ within a given projected radius, for three
    different reconstructions of a simulated lens (sim) from
    Space~Warps.  In each panel, the dashed blue curve is the correct
    answer.  The orange band represents the statistical ensemble from
    SpaghettiLens, the red line being the ensemble mean.  Locations of
    images (maximum, saddle point, minimum) are marked with vertical
    arrows.  Crossing the horizontal $\kappa=1$ line is the effective
    Einstein radius, and is so labelled. The upper panel is from
    K\"ung et al., (2015) (see Figure~3 of that paper).  The middle
    panel is the result when the innermost mass tile is replaced by 9
    smaller tiles.  The lower panel results from replacing each of the
    innermost 9 tiles each with 9 smaller tiles.}
  \label{fig:subsampling}
\end{figure}

@@

The models of simulated lenses in \cite{2015MNRAS.447.2170K} showed a
tendency to be too shallow.  Allowing smaller mass tiles in the
central region, thus allowing the pass profile to rise more steeply
near the centre, was suggested as a possible cure.

Figure~\figref{subsampling} shows an experiment with smaller mass
tiles in the inner region.  Replacing the very central mass tile with
9 smaller tiles allows for steeper central profiles.  Doing the same
for the 21 innermost mass tiles \todo{Check meaning of hires
  parameters.} solves the problem completely, but doubles the
computation time.  The main modelling work in this paper was, however,
done before the experiments with smaller mass tiles was complete.
Hence the results in this paper use the intermediate option
(corresponding to the middle panel in Figure~\figref{subsampling}).
As the results in this paper mainly concern the enclosed mass in the
outer regions, the remaining shallowness in the central region should
be inconsequential.
